\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage{geometry}%
\geometry{tmargin=2cm,lmargin=2cm,rmargin=2cm,bmargin=2cm}%
\usepackage[table]{xcolor}%
%
\usepackage{datetime2}%
\usepackage{listings}%
\title{CRIFX Contest Preparation Status Report}%
\date{Compiled \today~at \DTMcurrenttime\DTMcurrentzone~for commit fc2980d2}%
%
\begin{document}%
\normalsize%
\maketitle%
\section{Submissions summary}%
\label{sec:Submissionssummary}%
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}%
\hline%
\rowcolor{cyan}%
&\multicolumn{6}{c}{{\tiny Solutions}}&\multicolumn{2}{|c|}{{\tiny Non-solutions}}&\\%
\hline%
\rowcolor{cyan}%
{\tiny Problem}&{\tiny Independent}&{\tiny Groups}&{\tiny c/c++}&{\tiny java/kotlin}&{\tiny python}&{\tiny Sum}&{\tiny WA}&{\tiny TLE}&{\tiny Test Files}\\%
\hline%
addtwonumbers&\cellcolor{red}1/3&\cellcolor{red}1/2&0&0&1&1&0&0&0\\%
\hline%
helloworld&\cellcolor{red}1/3&\cellcolor{green}2/2&0&1&1&2&1&0&5\\%
\hline%
\end{tabular}

%
\section{Manual review tracking}%
\label{sec:Manualreviewtracking}%
\begin{tabular}{|l|c|c|c|}%
\hline%
\rowcolor{cyan}%
{\tiny Problem}&{\tiny Statement}&{\tiny Validator(s)}&{\tiny Data}\\%
addtwonumbers&\cellcolor{red}0/3&\cellcolor{red}0/2&\cellcolor{red}0/2\\%
\hline%
helloworld&\cellcolor{green}3/3&\cellcolor{red}1/2&\cellcolor{green}2/2\\%
\hline%
\end{tabular}

%
\section{How can I help?}%
\label{sec:HowcanIhelp?}%
\begin{enumerate}%
\item%
addtwonumbers needs at least 2 more AC submissions from people other than Finn Lidbetter.%
\item%
helloworld needs at least 2 more AC submissions from people other than Finn Lidbetter.%
\item%
addtwonumbers needs at least one more AC submission from any of the following language groups: c/c++ or java/kotlin.%
\item%
addtwonumbers needs at least one TLE submission.%
\item%
helloworld needs at least one TLE submission.%
\item%
addtwonumbers needs at least one WA submission.%
\item%
Add test data%
\item%
Add input validators%
\item%
Review problem statements%
\item%
Review test data%
\item%
Review input validators%
\end{enumerate}

%
\newpage%
\section{addtwonumbers}%
\label{sec:addtwonumbers}%
\subsection{Problemtools verifyproblem output}%
\label{subsec:Problemtoolsverifyproblemoutput}%
Including problemtools verifyproblem output is disabled for this problem. It can be enabled in the crifx{-}problem{-}status.toml file for this problem.

%
\subsection{Test Cases}%
\label{subsec:TestCases}%
Test case descriptions are rendered below if they exist. Otherwise, the first 10 lines of input are rendered if they each have at most 90 characters.%

%
\newpage%
\section{helloworld}%
\label{sec:helloworld}%
\subsection{Problemtools verifyproblem output}%
\label{subsec:Problemtoolsverifyproblemoutput}%
null

%
\subsection{Test Cases}%
\label{subsec:TestCases}%
Test case descriptions are rendered below if they exist. Otherwise, the first 10 lines of input are rendered if they each have at most 90 characters.%
\begin{itemize}%
\item%
sample{-}1%
\item%
001{-}finn%
\lstinputlisting[basicstyle=\footnotesize,backgroundcolor=\color{lightgray},framexleftmargin=1em,framexrightmargin=1em]{/Users/finn/git/crifx/examples/example_problemset/helloworld/data/secret/001-finn.desc}%
\item%
005{-}mrthompson%
\lstinputlisting[basicstyle=\footnotesize,backgroundcolor=\color{lightgray},framexleftmargin=1em,framexrightmargin=1em]{/Users/finn/git/crifx/examples/example_problemset/helloworld/data/secret/005-mrthompson.desc}%
\item%
010{-}shortest%
\item%
015{-}longest%
\end{itemize}

%
\end{document}